The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-18 paper2_JNLS/paper.tex
NM

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in PNAS for the sake of brevity.
\item Provide additional experimental measurements not presented in Bolles PRF. For example, statistics on surface slope and autocorrelation.
\end{itemize}

@@

%\bibliographystyle{plain}
%\bibliography{Notesbib}

>>>>

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in \cite{majda2019statistical} for the sake of brevity.
\item Provide additional experimental measurements not presented in \cite{bolles2019anomalous}. For example, statistics on surface slope and autocorrelation.
\end{itemize}

@@

\section*{Acknowledgements}
CTB acknowledges support from the IDEA grant at Florida State University, as well as from the Geophysical Fluid Dynamics Institute. 
MNJM acknowledges support from the Simons Foundation, award 524259.

\bibliographystyle{plain}
\bibliography{wavesbib}
